### 2017-07-21 Dokumentation/1_Paper/Paper.tex
kleine Aenderungen an Linkf fuer American Store

\begin{appendix}
\section{Anhang}
\todo{Autor: Svenja}
	Anhang mit Lizenzen usw.
\end{appendix}

------
3D-Object - American Store:
---
tutorial:

https://www.youtube.com/watch?v=3jJGBzAxXKo
---
used textures (all licences acquired):
(last viewed: yyyy-mm-dd)

@@

soilsand:
https://www.textures.com/download/soilsand0210/61549?q=soilsand0210
(last viewed: 2017-07-14)
---
used normalmap:

all normalmaps were created out of the respective textures using 'http://cpetry.github.io/NormalMap-Online/'
(last viewed: 2017-07-14)
------

>>>>

\begin{appendix}
\section{Anhang}
\todo{Autor: Svenja}
	Anhang mit Lizenzen usw.

\subsection{3D-Objekte}

\subsubsection{American Store}

\textbf{used textures (all licences acquired):}
(last viewed: yyyy-mm-dd)

@@

soilsand:
https://www.textures.com/download/soilsand0210/61549?q=soilsand0210
(last viewed: 2017-07-14)
---
\textbf{used normalmap:}

all normalmaps were created out of the respective textures using 'http://cpetry.github.io/NormalMap-Online/'
(last viewed: 2017-07-14)

\end{appendix}
